A thesis draft

### 2018-10-25 res/sections/10-ProjectAnalysis.tex
Add additional Harbor content

\subsubsection{Harbor} \todo{Talk about harbor!}
Started as a Virtual VNFM (Network Function Virtualization Manager) for 
Openbaton, during the project it has been expanded to become a complete 
replacement of the original product, adding the possibility to manage Network 
Services and to update the route tables, Roulette Controller (the tool 
description can be found in \todo{Insert roulette ref!}).

>>>>

\subsubsection{Harbor}
Started as a VNFM (Virtual Network Function Virtualization Manager) to offer 
a bridge for Openbaton to interact with Kubernetes, during the project it has 
been expanded to become a complete replacement of the original product, adding 
the possibility to manage Network Services and to update the routing tables 
contained in the Roulette Controller (the tool description can be found below
in~\ref{chap:prjan:sec:tech:sub:SFC:sub:roulette}). Harbor doesn't have a web 
interface, but it has a RESTful API that allow users to interact with him 
using CRUD operations. It offers functionalities similar to Openbaton: 
possibility to upload VNF definitions (basically, Kuberentes YAML deployments), 
and possibility to upload NS definitions. When an NS is saved, a consistency 
check is performed to assure that alle the VNF are already present in Harbor. 
Similarly to Openbaton an NS is deployed, all the associated VNFs are deployed 
with it, making the whole operation atomic from the user point-of-view. 
What Openbaton doesn't do is a smart resource utilization: Harbor, in fact, 
during NS is deletion, it checks if any related VNF remains orphan (which means 
without any NS using it). In that case the VNF will enter in a state of 
pruning: after five minutes, if the VNF has not be reutilized by another NS it 
will be deleted. This mechanism assure faster deployments in environments where 
NSs are continuously launched and deleted.

\subsection{SFC}

\subsubsection{Roulette Controller}
\label{chap:prjan:sec:Stech:sub:SFC:sub:roulette}

\subsubsection{Astaire}

\subsubsection{Ironhide}
